A Privacy Aware Mobile Sensor Application

### 2015-01-26 paper.tex
references changed paper title changed changed title of section 4.2 abstract added

\title{Privacy Analysis of a Mobile Sensor Application}
\author{Heinrich Hartmann \and Tim Wambach \and Maximilian Meffert \and R\"udiger Grimm}
\institute{University of Koblenz-Landau}
\maketitle

@@

\TODO{(later)}

@@

In this scenario we focus our attention to only one asset: The privacy of the citizen. Our definition of privacy is described in detail in Section \ref{sec:privacydef},

@@

\subsection{Step 2. Potential Analysis}
\label{subsec:pot-analysis}

The \emph{Potential Analysis} displays the intended and unintended interactions of the components in the world view.

>>>>

\title{A Privacy Aware Mobile Sensor Application}
\author{Heinrich Hartmann \and Tim Wambach \and Maximilian Meffert \and R\"udiger Grimm}
\institute{University of Koblenz-Landau}
\maketitle

@@

In our research work we have implemented a privacy aware mobile sensor application [diesen ersten Satz ggf. wieder streichen]. In this paper we outline a scenario of a mobile traffic survey and analyse its privacy risks according to a reference model for IT security analysis. This leads to concrete recommendations for privacy protecting measures that are implemented in the system, for example a Web-based dashboard which allows the users to view, modify and delete all personal data that is stored in the system.

@@

In this scenario we focus our attention to only one asset: The privacy of the citizen. Our definition of privacy is described in detail in Section \ref{sec:privacydef}.

@@

\subsection{Step 2. Potential World Analysis}
\label{subsec:pot-analysis}

The \emph{Potential World Analysis} displays the intended and unintended interactions of the components in the world view.
